### 2022-03-29 src/text/4-project.tex
add technical infrastructure

In this section, we provide an overview of the organization of the Gammapy project. We briefly describe the main roles and responsibilities, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality open source software. We also describe how we tackle with the software distribution, our solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes, and the tools we use to foster the Gammapy community and to provide user support. This section concludes with an outlook on the roadmap for future directions.

@@

\begin{itemize}
	\item GitHub repositories 
	\begin{itemize}
		\item gammapy (describe gammapy codebase)
		\item docs
		\item web
		\item data
		\item benchmarks
		\item recipes
		\item extra
		\item meetings
		\item conferences contributions
		\item catalogs? (i.e. gamma-cat)
		\item paper
	\end{itemize}
	\item github actions and automated tasks 
	\begin{itemize}
		\item ci
		\item docs
		\item benchmarks-slack
		\item codemeta.json and zenodo
		\item release-web
	\end{itemize}	
	\item pytest and code coverage in ci
	\item tests on docstrings and on code in rst files
	\item code quality services (codecov, lgtm, codacy)
	\item validation and benchmarks -validation as online appendix...?
\end{itemize}

@@

@@

Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
\begin{verbatim}
m = Map.read(“diffuse.fits”)
m.plot_interactive()
\end{verbatim}

@@

\begin{itemize}
	\item weekly developers calls
	\item coding sprints 
	\item slack
	\item github discussions
	\item gammapy recipes repo
	\item mailing lists 
		\begin{verbatim}
		gammapy-coordination-l@in2p3.fr 
		gammapy@googlegroups.com 
		gammapy-cta-l@in2p3.fr
		\end{verbatim}
	\item twitter
\end{itemize}

>>>>

In this section, we provide an overview of the organization of the Gammapy project. We briefly describe the main roles and responsibilities within the team, as well as the technical infrastructure designed to facilitate the development and maintenance of Gammapy as a high quality software. We use common tools and services for software development of Python open-source projects, code review, testing, package distribution and user support, with a customized solution for a versioned thoroughly tested documentation in the form of user-friendly playable recipes. This section concludes with an outlook on the roadmap for future directions.

@@

Gammapy follows an open-source and open-contribution development model based on the cloud repository service GitHub. A GitHub organization \textit{gammapy} \footnote{\url{https://github.com/gammapy}} hosts different repositories related with the project. The software codebase may be found in the \textit{gammapy} repository (see Table~\ref{table:codestats:data} and Figure~\ref{fig:codestats:lang} for code lines statistics). We make extensive use of the pull request system to discuss and review code contributions.

@@

Several automatized tasks are set as GitHub actions \footnote{\url{https://github.com/features/actions}}, blocking the processes and alerting developers when fails occur. This is the case of the content integration workflow, which monitors the execution of the test coverage suite \footnote{\url{https://pytest.org}} using datasets from the \textit{gammapy-data} repository. Tests scan not only the codebase but also the code snippets present in docstrings of the scripts and in the RST documentation files, as well as in the tutorials provided in the form of Jupyter notebooks.

Other automatized tasks, executing in the \textit{gammapy-benchmarks} repository, are responsible for numerical validation tests and benchmarks monitoring. Also tasks related with the release process are partially automatized, and every contribution to the codebase repository triggers the documentation building and publishing workflow within the \textit{gammapy-docs} repository (see Sec. ~\ref{ssec:software-distribution} and Sec. ~\ref{ssec:documentation}).

This small ecosystem of interconnected up-to-date repositories, automatized tasks and alerts, is just a part of a bigger set of GitHub repositories, where most of them are related with the project but not necessary for the development of the software (i.e. project webpage, complementary high-energy astrophysics object catalogs, coding sprints and weekly developer calls minutes, contributions to conferences, other digital assets, etc.) Finally, third-party services for code quality metrics are also set and may be found as status shields in the codebase repository.

@@

@@

\begin{itemize}
	\item web and on-line documentation 	
	\item slack
	\item github discussions
	\item weekly developers calls
	\item coding sprints 
	\item gammapy recipes repo
	\item mailing lists 
		\begin{verbatim}
		gammapy-coordination-l@in2p3.fr 
		gammapy@googlegroups.com 
		gammapy-cta-l@in2p3.fr
		\end{verbatim}
	\item twitter
\end{itemize}
